### 2014-03-01 thesis/src/chapters/chapter-state-of-the-art.tex
Thesis: refinements

Before delving into more detailed description it is vital to introduce most important terms used in \emph{Carina} documentation to depict this product:
\begin{itemize}
  \item Environment -- a collection of VMs in a master-slave configuration,
  \item Service -- a consumer of cloud resources. Each service can have its own environment configurations and create environments and control them independently of other services,
  \item Pools -- various clusters or virtual data centers in OpenNebula that can be targets for creating an environment
\end{itemize}

@@

\emph{Time-based} policies defines how the system should react in the given window frame(s). In each frame we can specify the minimum number of virtual machines that comprises an environment. On the other hand, \emph{load-based} policies define the way the system reacts to \textbf{average cpu usage} by the environment. This is the simplest \emph{threshold-model} as introduced in chapter 2. The user enters predicates which are evaluated against data gathered by OpenNebula and execute scaling actions  (\emph{scaleup} and \emph{scaledown}) if they are true. What is more, the minimal and maximal number of virtual machines must be specified. At present the only parameter that is taken into account while performing actions triggered by \emph{load-based} policies is cpu usage.

@@

\subsubsection{Scaling}
Chapter 3 introduced and discussed various types of application scaling. \emph{Carina} offers only one type of scaling and this is \emph{horizontal} scaling -- user's capabilities are limited only to add/remove a virtual machine to/from a given environment. Unfortunately there are no means to modify the parameters of a given or a set of virtual machines.

@@

There are number of things that cause concern:
\begin{asparaenum}
\item[\textbf{Persistency}] No one knows for what reason, but \emph{Carina} uses two databases. What makes things even worse, they completely differ in types, as \emph{MySQL} is a relational and \emph{redis} is a nosql database. This places additional burden on technical requirements of the platform.
\item[\textbf{Usage of Apache}] To work properly, \emph{Carina} needs Apache http server. In the server cgi-bin directory there are placed bash scripts which are invoked by contextualization scripts executed in different stages of virtual machines life cycle. Instead, we recommend setting proper web services, environment-agnostic, in a central node which can be run next to global scheduler.
\item[\textbf{User accounts}] \emph{Carina} forces the creation of a system-wide user for each service. These concepts should be totally independent.
\item[\textbf{Provisioning}] User has to use in the environment specification previously defined OpenNebula images. Their further adjusting happens in the contextualization phase. This forces the user to modify the state of a virtual machine when there is a need to perform any changes, for example in the software stack. Instead we suggest using some provisioning software such as puppet or chef -- this would enable users to change software stack only in configuration files (recipes) not by altering the virtual machine state.
\end{asparaenum}

@@

\subsubsection{Scalability}
\emph{Cloud foundry} supports only horizontal scaling not only within one provider, but also across many. This feature is called \emph{Multi-Cloud} in Cloud Foundry nomenclature.

>>>>

Before delving into a more detailed description it is vital to introduce most important terms used in \emph{Carina} documentation to depict this product:
\begin{itemize}
  \item Environment -- a collection of VMs in a master-slave configuration,
  \item Service -- a consumer of cloud resources. Each service can have its own environment configurations and create environments and control them independently of other services,
  \item Pools -- various clusters or virtual data centers in OpenNebula that can be targets for creating an environment
\end{itemize}

@@

\emph{Time-based} policies defines how the system should react in the given window frame(s). In each frame we can specify the minimum number of virtual machines that comprises an environment. On the other hand, \emph{load-based} policies define the way the system reacts to \textbf{average cpu usage} by the environment. This is the simplest \emph{threshold-model} as introduced in section 2.1.3. The user enters predicates which are evaluated against data gathered by OpenNebula and execute scaling actions  (\emph{scaleup} and \emph{scaledown}) if they are true. What is more, the minimal and maximal number of virtual machines must be specified. At present the only parameter that is taken into account while performing actions triggered by \emph{load-based} policies is cpu usage.

@@

\subsubsection{Scaling}
Section 2.2 introduced and discussed various types of application scaling. \emph{Carina} offers only one type of scaling and this is \emph{horizontal} scaling -- user's capabilities are limited only to add/remove a virtual machine to/from a given environment. Unfortunately there are no means to modify the parameters of a given or a set of virtual machines.

@@

There are number of things that cause concern:
\begin{asparaenum}
\item[\textbf{Persistency}] No one knows for what reason, but \emph{Carina} uses two databases. What makes things even worse, they completely differ in types, as \emph{MySQL} is a relational and \emph{redis} is a nosql database. This places additional burden on technical requirements of the platform.
\item[\textbf{Usage of Apache}] To work properly, \emph{Carina} needs Apache http server. In the server cgi-bin directory there are placed bash scripts which are invoked by contextualization scripts executed in different stages of virtual machines life cycle. Instead, we recommend setting proper web services, environment-agnostic, in a central node which can be run next to global scheduler.
\item[\textbf{User accounts}] \emph{Carina} forces the creation of a system-wide user for each service. These concepts should be totally independent.
\item[\textbf{Provisioning}] User has to use in the environment specification previously defined OpenNebula images. Their further adjustment happens in the contextualization phase. This forces the user to modify the state of a virtual machine when there is a need to perform any changes, for example in the software stack. Instead we suggest using some provisioning software such as puppet or chef -- this would enable users to change software stack only in configuration files (recipes) not by altering the virtual machine state.
\end{asparaenum}

@@

\subsubsection{Scalability}
\emph{Cloud foundry} supports horizontal scaling not only within one provider, but also across many. This feature is called \emph{Multi-Cloud} in Cloud Foundry nomenclature.
